---
title: "Nutria Presentation"
author: Alex, Austin, Clarissa, Cullen
date: 2021-08-27
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

# Goal
- **Reproduce the nitrate and potassium plot for Hurricane Hugo in Luquillo, Puerto Rico.**
- Investigate broader hurricane impact on stream chemistry data.

---

# Project Set-up & Team Organization [Alex]


---

# Step 1: Save data, create repository, repository structure [Clarissa]


---

# Step 2: Load libraries

We knew we'd need the standard libraries we've been working with for data wrangling and plotting. We started with tidyverse, here, and janitor.
```{r, results=FALSE}
library(tidyverse)
library(here)
library(janitor)
```

Later on in the data wrangling process, we realized we would need a few additional packages. `lubridate` facilitated the use of date data, and we used `patchwork` to compile faceted graphs.
```{r, results=FALSE}
library(lubridate)
library(patchwork)
```

---

# Step 3: Read & Munging Data [Cullen]


---

# Step 4: Creating Initial Plots [Austin]


---

# Step 5: Beautify-ing Plots & Pair Programming [Clarissa]


---

# Results [Cullen]


---

# Repository 
(just a link)


---

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr/), and [R Markdown](https://rmarkdown.rstudio.com).
